Reproducibility and plant pathology: where do we stand and a way forward

### 2021-06-16 analysis/paper/paper.Rmd
Specify figure paths in figure chunks

knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.path = "../figures/",
  dev = c("postscript"),
  fig.width = 3.31,
  fig.height = 3.31,
  out.width = "100%",
  dpi = 300,
  comment = "#>",
  dev = "cairo_pdf",
  cache = TRUE
)
```

>>>>

knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  dev = c("postscript"),
  fig.width = 3.31,
  fig.height = 3.31,
  out.width = "100%",
  dpi = 300,
  comment = "#>",
  dev = "cairo_pdf",
  cache = TRUE
)
```
